Motional Ground State Cooling Outside the Lamb-Dicke Regime

### 2017-08-09 geometry.tex
New figure 1 version 2 =)

  \fill[left color=red!50!black,right color=red!50!black,middle color=red!43,
  shading=axis,rotate=-50,shading angle=32]
  plot[domain={-1}:{1}, smooth, variable=\y] ({sqrt((\y)^2 + (\waist)^2) * \xscale}, \y * \theight)
  arc (0:180:\radiush cm and \radiusv cm)
  -- plot[domain={-1}:{1}, smooth, variable=\y] ({-sqrt((\y)^2 + (\waist)^2) * \xscale}, -\y * \theight)
  arc (180:360:\radiush cm and \radiusv cm);

@@

  \fill[left color=red!50!black,right color=red!50!black,middle color=red!43,
  shading=axis,rotate=-50,shading angle=40]
  plot[domain={-1}:{0}, smooth, variable=\y] ({sqrt((\y)^2 + (\waist)^2) * \xscale}, \y * \theight)
  arc (0:180:{(\radiush)*(\waist)} and {(\radiusv)*(\waist)})
  -- plot[domain={0}:{1}, smooth, variable=\y] ({-sqrt((\y)^2 + (\waist)^2) * \xscale}, -\y * \theight)
  arc (180:360:\radiush cm and \radiusv cm);
  \fill[red!50!gray,rotate=-50]
  ({-sqrt(1 + (\waist)^2) * \xscale}, -\theight*1.05)
  arc (180:{360+180}:\radiush cm and \radiusv cm);

  \path (-140:\theight) node[white] {\Large \textbf{Tweezer}};
\end{tikzpicture}

>>>>

  \fill[left color=red!50!black,right color=red!50!black,middle color=red!43,
  shading=axis,rotate=-45,shading angle=32]
  plot[domain={-1}:{1}, smooth, variable=\y] ({sqrt((\y)^2 + (\waist)^2) * \xscale}, \y * \theight)
  arc (0:180:\radiush cm and \radiusv cm)
  -- plot[domain={-1}:{1}, smooth, variable=\y] ({-sqrt((\y)^2 + (\waist)^2) * \xscale}, -\y * \theight)
  arc (180:360:\radiush cm and \radiusv cm);

@@

  \fill[left color=red!50!black,right color=red!50!black,middle color=red!43,
  shading=axis,rotate=-45,shading angle=40]
  plot[domain={-1}:{0}, smooth, variable=\y] ({sqrt((\y)^2 + (\waist)^2) * \xscale}, \y * \theight)
  arc (0:180:{(\radiush)*(\waist)} and {(\radiusv)*(\waist)})
  -- plot[domain={0}:{1}, smooth, variable=\y] ({-sqrt((\y)^2 + (\waist)^2) * \xscale}, -\y * \theight)
  arc (180:360:\radiush cm and \radiusv cm);
  \fill[red!50!gray,rotate=-45]
  ({-sqrt(1 + (\waist)^2) * \xscale}, -\theight*1.05)
  arc (180:{360+180}:\radiush cm and \radiusv cm);

  \path (-135:\theight) -- ++(-0.2, 0) node[white] {\Large \textbf{Tweezer}};
\end{tikzpicture}
